%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 \usepackage{fontawesome}
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Sayantan}{Pal}{ \urlstyle{same}\href{https://www.linkedin.com/in/sayantan-pal-54a967205/}{Linkedin: sayantanpal}| 
\href{mailto:pal.8@iitj.ac.in}{pal.8@iitj.ac.in} | 9318327900 | 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{IIT Jodhpur}
\descript{BTech. in  Mechanical ENGG.}
\location{Dec 2023(Expected) | Jodhpur, IN}
\location{ CGPA: 8.02 / 10.0(upto 4th sem) \\}
\sectionsep

\subsection{MVN,Aravali Hills}
\location{Grad. May 2019|  Faridabad, India}
\location{ Class XII:- 93.0\% \\}
\location{Class X:-92.4\% \\}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\subsection{Languages}
\textbullet{} C \textbullet{}   C++ \textbullet{} Python 
\textbullet{} Dart \\ \textbullet{} Javascript  \textbullet{}  Matlab \textbullet{}Latex \\
\sectionsep
\subsection{Development}

\textbullet{} OpenCV \textbullet{} Tensorflow \textbullet{} Natural Language processing(NLP) \textbullet{} Keras \\
\textbullet{} Nodejs \textbullet{} ReactJs  \textbullet{} CSS 
\textbullet{} HTML5 \\ \textbullet{} Bootstrap \textbullet{} PassportJs\textbullet{} EJS  \\
\textbullet{} MongoDb \textbullet{} SQl \textbullet{} Git \textbullet{} Github \\ \textbullet{} Firebase \textbullet{} Heroku  \\
\sectionsep
\subsection{Other Skills}

\textbullet{} Solidworks \textbullet{}Auto CAD \\  \textbullet{} 
Competitive programming \textbullet{} Essay writing \textbullet{} Instrumental Music(piano)\\
\sectionsep





\section{Coursework}

\subsection{Under Graduate}
\textbullet{}Introduction to  Machine Learning \\
\textbullet{}Introduction to python programming\\
\textbullet{}Data structures and algorithms \\
\textbullet{}Signals and Systems\\
\textbullet{}Scientific computations\\
\textbullet{}Engineering realisation \\
\textbullet{}Intro to electrical engineering \\
\textbullet{}Manufacturing processes\\
\sectionsep
\subsection{Udemy}
\textbullet{}Flutter & Dart - The Complete Guide \\
\textbullet{}Deep Learning and Computer Vision A-Z™: OpenCV, SSD & GANs\\
\textbullet{}The Complete 2021 Web Development Bootcamp\\
\textbullet{}Data Science and Machine Learning Bootcamp\\
\textbullet{}Machine Learning A-Z™: Hands-On Python & R In Data Science\\
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\runsubsection{Sunbeam Auto}
\descript{| Vocational training }
\location{Dec 2019 - Jan 2019 | Gurgaon, Haryana}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}

\item Actively took part in day to day processes across multiple departments namely Alloying,PDC,GDC,Machining Department and tool room. 
\item Deduced ways to reduce Rejection ratio and downtime of machines especially in the PDC department.
\item Took part in assessing the performance of Robotic Arm(Yuzumi) to reduce Operational cost in the Machining department.
\item Created the G-code to be fed to the VMC machines for various Tool designs running on the shop floor then.
\end{tightemize}

\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{\href{https://github.com/psayantan29/Course-Project-IML-CSL2010}{Empirical Analysis Of General Utility Problem In Machine Learning}}
\descript{| Course Project}
\location{December 2020 - January 2021 | \href{https://github.com/psayantan29/Course-Project-IML-CSL2010}{\bf GitHub \faExternalLink}}\location{}
\item •Self-implementation of Multi-Layer Perceptron Neural Network,Decision tree induction method and Analysis of it to find the presence of general utility problem on different domains such as DNF2 and flag domain.
\item •Worked out new ways to reduce overfitting, finding the optimal bias, variance and Bayes optimal classification error to extract max performance from the model.\newline
• Tech-stack:\textbf{Python,Scikit-Learn}

\sectionsep
\runsubsection{ \href{https://fathomless-wave-33794.herokuapp.com}{Quick Learner \faExternalLink}}
\descript{| Developer}
\item •Built an dynamic online educational website with Nodejs for backend alongside EJS as templating engine and MongoDb as database.Encrypted Sensitive information with level 6 encryption. Used Nodemailer module to send email from server and hosted the website on Heroku.
\item •Integrated Google Authentication with the use of passport.js as the  authentication middleware alongside using Razorpay Payment Gateway for accepting payments from customers for purchases.\newline
  • Tech-stack: \textbf{NodeJS,MongoDB,CSS,Javascript}
\sectionsep

\runsubsection{PARKING ALLOCATION
SYSTEM}
\descript{| Engineering Design}
\location{September 2019 - July 2020}
\item •Led a team of 8 members to conceptualise and work on a Self sustained parking allocation system to be operated in large closed and open parking spaces.
\item •Successfully developed working prototype and online allocation system to be implemented on large scale. Used TEG in the prototype to achieve self sustainability.

• Tech-stack: \textbf{Solidworks,Arduino,SQL}

\section{Links} 
\textbullet LinkedIn:  \href{https://www.linkedin.com/in/sayantan-pal-54a967205/}{\bf Sayantan pal \faExternalLink} \hspace{1.5cm}
\textbullet Codechef : \href{https://www.codechef.com/users/vectus_pirate}{\bf vectus pirate \faExternalLink} \\
\textbullet Hackerrank:  \href{https://www.hackerrank.com/psayantan29}{\bf psayantan29 \faExternalLink} \hspace{1cm}
\textbullet Github:  \href{https://github.com/psayantan29}{\bf psayantan29 \faExternalLink}

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements} 
\begin{tabular}{rll}
2019	     & Among top 0.6 \% percentile of 1.3 million Applicants in JEE Advanced -2019 \\
2019        & Achieved AIR-197 amongst 0.2 million applicants in WBJEE-2019\\ 
2019	     & Amongst top 0.4 \% percentile of 0.2 million Applicants in BITSAT -2019 \\

\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\end{document}  \documentclass[]{article}
